mixchar

### 2018-08-08 manuscript/manuscript.Rnw
modify size of plot in manuscript
revise authors, add packages, add version requirement

\section*{Paper Authors}
1. Windecker, Saras M. \\
2. Vesk, Peter A. \\
3. Trevathan-Tackett, Stacey M. \\
4. Catford, Jane A. \\
5. Macreadie, Peter I. \\
4. Golding, Nick.

\section*{Paper Author Roles and Affiliations}
1. PhD Candidate, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
4. Assistant Professor, Biological Sciences, University of Southampton, Highfield Campus, Southampton SO17 1BJ, UK \\
5. Associate Professor, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
6. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia

@@

<<eval = FALSE>>=
plot(deriv_juncus)
@

@@

<<fig.cap = '\\label{Fig:decon} Deconvolution of \\textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.', out.width = '0.7\\linewidth', asp = 1, fig.align = 'center'>>=
par(mar = c(5,5,1,1))
plot(output_juncus, bw = FALSE)
@

@@

@@

\section*{Programming language}
R version XXX or higher.

@@

\section*{Dependencies}
R packages: \verb|minpack.lm|, \verb|nloptr|, \verb|tmvtnorm|, \verb|zoo|.

@@

\section*{Acknowledgements}
The authors would like to thank Dr. Nick Tierney for reviewing an early version of the package. We would like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR. Vegetation collection for data used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429. We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens.

>>>>

\section*{Paper Authors}
1. Windecker, Saras M. \\
2. Vesk, Peter A. \\
3. Trevathan-Tackett, Stacey M. \\
4. Golding, Nick.

\section*{Paper Author Roles and Affiliations}
1. PhD Candidate, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
2. Associate Professor, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia \\
3. Research Fellow, Centre for Integrative Ecology, School of Life and Environmental Sciences, Deakin University, Burwood Campus, Burwood VIC 3124, Australia \\
4. Research Fellow, School of BioSciences, University of Melbourne, Parkville VIC 3010, Australia

@@

<<eval = FALSE>>=
plot(deriv_juncus, cex = 2)
@

@@

<<fig.cap = '\\label{Fig:decon} Deconvolution of \\textit{Juncus amabilis} example dataset. Mass loss data overlaid with output of deconvolution. Rate of mass loss scaled by initial mass of sample.', out.width = '0.7\\linewidth', asp = 1, fig.align = 'center'>>=
plot(output_juncus, bw = FALSE)
@

@@

<<>>=
stt <- read.table("../mixchar.notes/USATtLeaf_data.txt", fill = TRUE, header = FALSE, skip = 46, skipNul = TRUE, fileEncoding="UTF-16LE")
colnames(stt) <- c("time", "temp", "weight", "deriv")
@

@@

\section*{Programming language}
R version 3.2.0 or higher.

@@

\section*{Dependencies}
R packages: \verb|graphics|, \verb|minpack.lm|, \verb|nloptr|, \verb|stats|, \verb|tmvtnorm|, \verb|zoo|.

@@

\section*{Acknowledgements}
The authors would like to thank Dr. Nick Tierney for reviewing an early version of the package. We would like to thank volunteers Paula Sanchez, Abbey Kinnish, Kelsey Johnson, Madeline Brenker, and Urtzi Enriquez Urzelai for assistance in the field collecting plant specimens. We would like to thank the University of Melbourne Department of Chemical and Biomolecular Engineering for access to and training on the TGA-FTIR. Vegetation collection for data used to build and verify the model was conducted under Victorian Department of Environment, Land, Water and Planning Permit No 10007429.
